Effects of rarefaction

### 2021-02-24 analysis/rev_prototyping/rarefaction.Rmd
fix pipeline

overall_skew_results <- adjusted_comparison %>%
  filter(s0_FALSE > 2, skew_unique_TRUE > 20, skew_unique_FALSE > 20) %>%
  mutate(high_skew_raw = skew_percentile_excl_FALSE > 95,
         high_skew_adjusted = skew_percentile_excl_TRUE > 95) %>%
  group_by(dat) %>%
  summarize(proportion_skew_high_raw = mean(high_skew_raw),
            proportion_skew_high_adjusted = mean(high_skew_adjusted),
            nsites_skew = dplyr::n())

overall_simpson_results <- adjusted_comparison %>%
   filter(simpson_unique_TRUE > 20, simpson_unique_FALSE > 20) %>%
  mutate(low_simpson_raw = simpson_percentile_FALSE < 5,
         low_simpson_adjusted = simpson_percentile_TRUE < 5) %>%
  group_by(dat) %>%
  summarize(proportion_simpson_low_raw = mean(low_simpson_raw),
            proportion_simpson_low_adjusted = mean(low_simpson_adjusted),
            nsites_simpson = dplyr::n())

overall_results <- left_join(overall_skew_results, overall_simpson_results)

ggplot(filter(adjusted_comparison, s0_FALSE > 2, skew_unique_TRUE > 20, skew_unique_FALSE > 20), aes(skew_percentile_excl_FALSE, skew_percentile_excl_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

ggplot(filter(adjusted_comparison, s0_FALSE > 2, skew_unique_TRUE > 20, skew_unique_FALSE > 20), aes(skew_percentile_excl_FALSE, skew_percentile_excl_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  facet_wrap(vars(dat))

overall_skew_results

ggplot(filter(adjusted_comparison, simpson_unique_TRUE > 20, simpson_unique_FALSE > 20), aes(simpson_percentile_FALSE, simpson_percentile_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

ggplot(filter(adjusted_comparison, simpson_unique_TRUE > 20, simpson_unique_FALSE > 20), aes(simpson_percentile_FALSE, simpson_percentile_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  facet_wrap(vars(dat)) 
overall_simpson_results
```

>>>>

overall_results <- adjusted_comparison %>%
  filter(s0_FALSE > 2, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)) %>%
  mutate(high_skew_raw = skew_percentile_excl_FALSE > 95,
         high_skew_adjusted = skew_percentile_excl_TRUE > 95,
         low_even_raw = simpson_percentile_FALSE < 5,
         low_even_adjusted = simpson_percentile_TRUE < 5,
         low_shannon_raw = shannon_percentile_FALSE <5,
         low_shannon_adjusted = shannon_percentile_TRUE < 5,
         high_singletons_raw = nsingletons_percentile_excl_FALSE > 95,
         high_singletons_adjusted = nsingletons_percentile_excl_TRUE > 95,
         low_singletons_raw = nsingletons_percentile_FALSE < 5,
         low_singletons_adjusted = nsingletons_percentile_TRUE < 5,
         high_po_raw = mean_po_comparison_percentile_FALSE > 95,
         high_po_adjusted = mean_po_comparison_percentile_TRUE > 95)

summary_vars <- colnames(overall_results)[ c(which(grepl("raw", colnames(overall_results))), which(grepl("adjusted", colnames(overall_results))))]

overall_results <- overall_results %>%
  group_by(dat) %>%
  summarize_at(summary_vars, mean)

# overall_simpson_results <- adjusted_comparison %>%
#    filter(log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)) %>%
#   mutate(low_simpson_raw = simpson_percentile_FALSE < 5,
#          low_simpson_adjusted = simpson_percentile_TRUE < 5) %>%
#   group_by(dat) %>%
#   summarize(proportion_simpson_low_raw = mean(low_simpson_raw),
#             proportion_simpson_low_adjusted = mean(low_simpson_adjusted),
#             nsites_simpson = dplyr::n())
# 
# overall_results <- left_join(overall_skew_results, overall_simpson_results)

overall_results

ggplot(filter(adjusted_comparison, s0_FALSE > 2, log_nparts_TRUE > log(20), log_nparts_FALSE > 20), aes(skew_percentile_excl_FALSE, skew_percentile_excl_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

ggplot(filter(adjusted_comparison, s0_FALSE > 2, log_nparts_TRUE > 20, log_nparts_FALSE > log(20)), aes(skew_percentile_excl_FALSE, skew_percentile_excl_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  facet_wrap(vars(dat))

ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(simpson_percentile_FALSE, simpson_percentile_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(simpson_percentile_FALSE, simpson_percentile_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  facet_wrap(vars(dat))

ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(shannon_percentile_FALSE, shannon_percentile_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(shannon_percentile_FALSE, shannon_percentile_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  facet_wrap(vars(dat))

ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(nsingletons_percentile_excl_FALSE, nsingletons_percentile_excl_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(nsingletons_percentile_excl_FALSE, nsingletons_percentile_excl_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  facet_wrap(vars(dat))

ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(mean_po_comparison_percentile_FALSE, mean_po_comparison_percentile_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(mean_po_comparison_percentile_FALSE, mean_po_comparison_percentile_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  facet_wrap(vars(dat))
